---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hw3packageWithRcpp)
```

## Introduction

Welcome to my `hw3packageWithRcpp` package!     

<<<<<<< HEAD
`hw3packageWithRcpp` is a package for generalized linear model and two related metrics.     
=======
`hw3packageWithRcpp` is a package for generalized linear model and related metrics.     
>>>>>>> a97c631 (two functions)

The function `lrm` can give the coefficients and the fitted value according to a matrix of covariates, response vector.     

The function `R2` compute R squared value using Rcpp.    

<<<<<<< HEAD
The function `mape` compute R mean absolute percentage error using Rcpp.    
=======
>>>>>>> a97c631 (two functions)

We will verify the correctness and efficiency of the 3 functions in this tutorial. 


## `lrm`

We verify the function `lrm`  with original function `glm` from R package `stats`.   

We use R buil-in data `mtcars` to verify this function. The first column `mpg` will be the response vector `y` and the rest of the columns will be `X`. 
```{r}
#response
mpg = mtcars[, 1]
#covariates
X = as.matrix(mtcars[, -1])
```

coefficients
```{r}
library(stats)
all.equal(as.vector(lrm(X, mpg)$beta), 
          as.vector(glm(mpg ~ ., data = mtcars, family = "gaussian")$coefficients))
```

fitted.values
```{r}
all.equal(as.vector(lrm(X, mpg)$y.fitted), 
          as.vector(glm(mpg ~ ., data = mtcars, family = "gaussian")$fitted.values))
```
Check the efficiency.
```{r}
library(bench)
plot(mark(as.vector(lrm(X, mpg)$beta), 
          as.vector(glm(mpg ~ ., data = mtcars, family = "gaussian")$coefficients)))
```

This shows that `lrm` is correct and more efficient than the original function.  


## `R2`
We simulate data with true value and fitted value from regression model.
```{r}
x = 1:1000
y = 5*x + rnorm(1000, 0, 1000)
fit = lm(y ~ x)
```

`R2_Score` from R package `MLmetrics` is used to check the correctness of the function.
Check the correctness.
```{r}
all.equal(R2(fit$fitted.values, y),
          MLmetrics::R2_Score(fit$fitted.values, y))
```
Check the efficiency.
```{r}
plot(mark(R2(fit$fitted.values, y),
          MLmetrics::R2_Score(fit$fitted.values, y)))
```

This shows that `R2` is correct and more efficient than the original function. 


